---
title: "Review2 - Accidents analysis"
output: 
  html_document: 
  fig_height: 4
highlight: pygments
theme: spacelab
---
### Reg. No: 18BCE1237
  
### Name: Aakash Ratha
  
## Setup

Sample
```{r}
library("dplyr")
library("ggplot2")
library("tidyr")
library("ggpubr")
```

```{r}
data = read.csv('US_Accidents_June20.csv')
head(data)
str(data)
```

```{r}
class(data)
summary(data)
```

```{r}
data %>%
  distinct(End_Lat)
data
data %>%
  distinct(End_Lng)
data
```
```{r}
colnames(data)
```

```{r}
data$Severity
data %>%
  distinct(Severity)
mean(data$Severity)
```

# Above output shows that on an average the severity of accidents in US is between 2-3 (mostly 2). Here 1 indicates the least impact on traffic and 4 indicates significant impact on traffic.

```{r}
data$Source
data %>%
  distinct(Source)
data %>%
  summarise(count=n_distinct(Source))
```

# There are 3 different sources of all these accident reports mentioned in this dataset.

```{r}
data %>%
  distinct(Distance.mi.)
mean(data$Distance.mi.)
```

# Average length of road extent affected by accidents in US is 0.2816167

```{r}
data %>%
  distinct(Number)
data %>%
  distinct(Street)
data %>%
  select(Number, Street)
data %>%
  filter(Number==2584) %>%
  select(Number, Street, Side)
data %>%
  filter(Number==2584 & Side=='R') %>%
  select(Number, Street, Side)
data %>%
  filter(Number==2584 & Side=='L') %>%
  select(Number, Street, Side)
data %>%
  filter(Number==376) %>%
  select(Number, Street, Side)
data %>%
  filter(Number==376 & Side=='R') %>%
  select(Number, Street, Side)
data %>%
  filter(Number==376 & Side=='L') %>%
  select(Number, Street, Side)

```

# If we consider street number 2584 and 376, more number of accidents have taken place on right hand side (Relative side). Similarly, we can perform same analysis for other street numbers as well.

```{r}
data %>%
  distinct(Visibility.mi.)
mean(data$Visibility.mi., na.rm = TRUE)
data %>%
  mutate(Visibility.mi.= replace(Visibility.mi., is.na(Visibility.mi.), mean(data$Visibility.mi., na.rm = TRUE)))
data = data%>%
  mutate(Visibility.mi.= replace(Visibility.mi., is.na(Visibility.mi.), mean(data$Visibility.mi., na.rm = TRUE)))
mean(data$Visibility.mi.)
```

# If we talk about the visibility, average visibility(in miles) is 9.122644

```{r}
data$State
data %>%
  distinct(State)
data %>%
  filter(State=='OH') %>%
  select(City, Street, Number)
data %>%
  filter(State=='OH') %>%
  summarise(n=n())
```

# There are almost 66k-67k accidents in state OH which is a huge number. Similarly in this way we can analyse for other states too. Now in OH state itself, we will filter city.

```{r}
data$City
data %>%
  distinct(City)
data %>%
  group_by(City) %>%
  summarise(n=n())
data %>%
  group_by(City) %>%
  summarise(n=n()) %>%
  filter(City=='Dayton')
```

# There are 14,251 accidents in Dayton out of 66k-67k in OH state. Similar analysis can be done for other cities too in OH state itself.

```{r}
data$Weather_Condition
data %>%
  distinct(Weather_Condition)
calculate_mode <- function(x) {
  uniqx <- unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
calculate_mode(data$Weather_Condition)
```

# Most of the accidents are reported in Clear conditions.

```{r}
max_state = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
max_state(data$State)
```

# Most number of accidents have occured in CA state.

```{r}
max_city = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
max_city(data$City)
```

# Highest number of accidents are reported in Houston city.

```{r}
min_city = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.min(tabulate(match(x, uniqx)))]
}
min_city(data$City)
```

# Tiro is the least affected city as far as accidents are concerned.

```{r}
min_state = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.min(tabulate(match(x, uniqx)))]
}
min_state(data$State)
```

# Minimum number of accidents have taken place in ND state.

```{r}
data$Temperature.F.
data %>%
  distinct(Temperature.F.)
mean(data$Temperature.F., na.rm = TRUE)
```

# Mean temperature is 61.935 in F.

```{r}
data$TMC
data %>%
  distinct(TMC)
data %>%
  summarise(n=n_distinct(TMC))
```

# There are total 22 different TMC (Traffic Message Channel) which gives more detailed description.

```{r}
min_TMC = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.min(tabulate(match(x, uniqx)))]
}
min_TMC(data$TMC)
```

# 351 is the TMC which has been reported least number of times.

```{r}
max_TMC = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
max_TMC(data$TMC)
```

# 201 is the TMC which has been reported most number of times.

```{r}
data$Zipcode
data %>%
  distinct(Zipcode)
data %>%
  summarise(n=n())
max_ZIP = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
max_ZIP(data$Zipcode)
```

# Maximum accidents reported zipcode - 91706

```{r}
min_ZIP = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.min(tabulate(match(x, uniqx)))]
}
min_ZIP(data$Zipcode)
```

# Minimum accidents reported zipcode - 43068-3402

```{r}
data %>%
  group_by(Zipcode) %>%
  summarise(n=n())
```

# Zipcode and number of accidents

```{r}
data$Wind_Chill.F.
data %>%
  distinct(Wind_Chill.F.)
mean(data$Wind_Chill.F., na.rm = TRUE)
data = data%>%
  mutate(Wind_Chill.F.= replace(Wind_Chill.F., is.na(Wind_Chill.F.), mean(data$Wind_Chill.F., na.rm = TRUE)))
mean(data$Wind_Chill.F.)
```

# Mean wind chill in F is 53.5573

```{r}
data$Number
data %>%
  distinct(Number)
data %>%
  group_by(Number) %>%
  summarise(n=n())
```

# Street number and number of accidents

```{r}
min_num = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.min(tabulate(match(x, uniqx)))]
}
min_num(data$Number)
```

# Minimum number of accidents - Street number 17520

```{r}
max_num = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
max_num(data$Number)
```

# Maximum number of accidents - Street number 1.

```{r}
data$Timezone
data %>%
  distinct(Timezone)
data %>%
  group_by(Timezone) %>%
  summarise(n=n())
```

# Timezone and reported number of accidents

```{r}
data %>%
  distinct(Description)
```

# Different type of description

```{r}
data$Airport_Code
data %>%
  distinct(Airport_Code)
data %>%
  group_by(Airport_Code) %>%
  summarise(n=n())
```

# Airport code and number of accidents

```{r}
max_code = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
max_code(data$Airport_Code)
```

# KMCZ is the nearest airport based weather station where most number of accidents have taken place.

```{r}
min_code = function(x) {
  uniqx = unique(na.omit(x))
  uniqx[which.min(tabulate(match(x, uniqx)))]
}
min_code(data$Airport_Code)
```

# KP58 is the nearest airport based weather station where min. number of accidents have taken place.

```{r}
data$Weather_Timestamp
data %>%
  distinct(Weather_Timestamp)
data %>%
  group_by(Weather_Timestamp) %>%
  summarise(n=n())
```

# Weather_Timestamp

```{r}
data$Humidity...
data %>%
  distinct(Humidity...)
data %>%
  group_by(Humidity...) %>%
  summarise(n=n())
mean(data$Humidity..., na.rm=TRUE)
```

# Humidity and number of accidents. Mean is 65.11427

```{r}
max_code(data$Humidity...)
min_code(data$Humidity...)
```

# Max and min accidents have taken place at 100% and 1% humidity respectively.

```{r}
data$Pressure.in.
data %>%
  distinct(data$Pressure.in.)
mean(data$Pressure.in., na.rm=TRUE)
```

# Mean pressure is 29.74463

```{r}
data$Wind_Direction
data %>%
  distinct(Wind_Direction)
data %>%
  group_by(Wind_Direction) %>%
  summarise(n=n())
```

# Wind_Direction and number of accidents

```{r}
max_code(data$Wind_Direction)
```

# When wind is calm, there are max. number of accidents reported so there's no point of any kind of wind direction.

```{r}
data$Wind_Speed.mph.
data %>%
  distinct(Wind_Speed.mph.)
data %>%
  group_by(Wind_Speed.mph.) %>%
  summarise(n=n())
```

# Wind_Speed and number of accidents

```{r}
mean(data$Wind_Speed.mph., na.rm=TRUE)
```

# Mean wind speed is 8.219025 mph

```{r}
data$Precipitation.in.
data %>%
  distinct(Precipitation.in.)
data %>%
  group_by(Precipitation.in.) %>%
  summarise(n=n())
```

# Precipitation and number of accidents

```{r}
mean(data$Precipitation.in., na.rm=TRUE)
```

# Mean precipitation is 0.01598256

```{r}
max_code(data$Precipitation.in.)
min_code(data$Precipitation.in.)
```

# Max accidents have taken place at 0 precipitation. Precipitation again does not make any sense

```{r}
data$Amenity
data %>%
  distinct(Amenity)
data %>%
  group_by(Amenity) %>%
  summarise(n=n())
```

# Accidents and presence of amenity

```{r}
data$Bump
data %>%
  group_by(Bump) %>%
  summarise(n=n())
```

# Very few accidents have occured in presence of Bump.

```{r}
data$Crossing
data %>%
  group_by(Crossing) %>%
  summarise(n=n())
```

# almost 3 lakh accidents have taken place in presence of Crossing.

```{r}
data %>%
  group_by(Junction) %>%
  summarise(n=n())
```

# Again, almost 3 lakh accidents have occured in presence of Junction.

```{r}
data %>%
  group_by(No_Exit) %>%
  summarise(n=n())
```

# 4384 accidents have taken place in presence of No_Exit.

```{r}
data %>%
  group_by(Give_Way) %>%
  summarise(n=n())
```

# 9564 accidents have taken place in presence of give_way.

```{r}
data %>%
  group_by(Railway) %>%
  summarise(n=n())
```

# Almost 32k accidents have taken place in presence of railway and this can be dangerous and can cause deaths.

```{r}
data %>%
  group_by(Roundabout) %>%
  summarise(n=n())
```

# At roundabout, 184 accidents have taken place.

```{r}
data %>%
  group_by(Stop) %>%
  summarise(n=n())
```

# Almost 52k accidents have occured in presence of Stop.

```{r}
data %>%
  group_by(Station) %>%
  summarise(n=n())
```

# 70k accidents in presence of station

```{r}
data %>%
  group_by(Turning_Loop) %>%
  summarise(n=n())
```

# No accidents reported in presence of turning loop.

