---
title: "Review2 - Accidents analysis"
output: 
  html_document: 
  fig_height: 4
highlight: pygments
theme: spacelab
---
### Reg. No: 18BCE1237
  
### Name: Aakash Ratha
  
## Setup
  
# Libraries
  
```{r}
library("ggplot2")
library("dplyr")
library("ggpubr")
library("tidyr")
```

# Importing the csv file

```{r}
data = read.csv('US_Accidents_June20.csv')
head(data)
```

```{r}
str(data)
```


```{r}
data %>%
  distinct(TMC)
calculate_mode <- function(x) {
  uniqx <- unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}
calculate_mode(data$TMC)
```

# 201 is the most frequent TMC reported.

```{r}
hist(data$TMC)
```
# Above is the histogram

```{r}
hist(data$Severity)
```
# Above is the histogram.

```{r}
# Correlation matrix
my_data = data[, c(4,7,8,11)]
res = cor(my_data)
round(res,2)
```
# Above is the correlation matrix

```{r}
data %>%
  summarise(n=n_distinct(Timezone))
data %>%
  group_by(Timezone) %>%
  summarise(n=n())
```

# There are 5 distinct timezones.
# According to the different timezones number of accidents occured.

```{r}
x = c(837122, 1484854, 200902, 986859)
labels = c('US/Central', 'US/Eastern', 'US/Mountain', 'US/Pacific')
piepercent = round(100*x/sum(x), 1)
pie(x, labels = piepercent, main="Timezone pie chart", col=rainbow(length(x)))
legend("topright", c('US/Central', 'US/Eastern', 'US/Mountain', 'US/Pacific'), cex = 0.8, fill = rainbow(length(x)))
```

# Timezone pie chart

```{r}
data %>%
  distinct(State)
data %>%
  group_by(State) %>%
  summarise(n=n())
```
# Number of accidents state-wise

```{r}
data %>%
  group_by(Side) %>%
  summarise(n=n())
x=c(633819, 2879797)
labels=c('L', 'R')
piepercent = round(100*x/sum(x), 1)
pie(x, labels = piepercent, main="Side pie chart", col=rainbow(length(x)))
legend("topright", c('L', 'R'), cex = 0.8, fill = rainbow(length(x)))
```

# Pie chart of Side wise accidents

```{r}
x = c(44625, 2012, 78584, 816825, 49731)
labels = c('AL', 'AR', 'AZ', 'CA', 'CO')
barplot(x, main="Accidents statewise", xlab="Number of accidents", ylab = "States", names.arg = labels, col="darkred", horiz = TRUE)
```

# Accidents statewise barplot

```{r}
data %>%
  filter(State=='OH') %>%
  group_by(City) %>%
  summarise(n=n())
```

# Accidents city-wise in state OH - Houston is the one in which max.accidents have taken place

```{r}
data %>%
  filter(City=='Houston') %>%
  summarise(n=n())
```

# 1,01,240 accidents took place in houston.

```{r}
data %>%
  group_by(Street) %>%
  summarise(n=n())
```

# Accidents taken place in the houston city and grouped streetwise.

```{r}
calculate_mode(data$Street)
```

# I-5 N road - max. accidents took place

```{r}
data %>%
  filter(City=='Houston') %>%
  select(Street)
```

# Streets in Houston

```{r}

```

#

```{r}

```



